---
title: "Test Document"
#author: "Aaron Gullickson"
format: 
   html:
     embed-resources: true
     toc: true
   pdf:
     keep-md: false
     keep-tex: false
execute:
  echo: true
---

```{r}
#| label: setup
#| echo: false
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(gt)
load("class_data/movies.RData")
```


## Markdown Syntax

This is text that will be in the body of the document. I can **bold** text, or I can *italicize* text.

### Here is a subheading

Outlines

-   Here is a point
-   Here is another point
    -   Here is a subpoint
    -   here is another subpoint
-   Back to the original points

1.  First thing
2.  Second thing
3.  Third thing

##### Here is a subsubheading

###### Here is a subsubsubheading

This is a paragraph. This is a paragraph. This is a paragraph. This is a paragraph. This is a paragraph. This is a paragraph. This is a paragraph. This is a paragraph. This is a paragraph. This is a paragraph. This is a paragraph.

```{r}
#| label: simple-r-output
mean(movies$runtime)
```

This is another paragraph. This is another paragraph. This is another paragraph. This is another paragraph. This is another paragraph. This is another paragraph. This is another paragraph. This is another paragraph.

```{r}
#| label: fig-movie-ratings
#| fig-cap: Comparison of anonymous IMDB user ratings to professional rater's movie scores.
#| fig-pos: "!t"
ggplot(movies, aes(x = rating_imdb, y = metascore))+
  geom_jitter(alpha = 0.6)+
  labs(x = "IMDB rating", y = "metascore")+
  theme_bw()
```

Take a look at @fig-movie-ratings and tell me what you see.

> I have sworn upon the altar of God, eternal hostility against every form of tyranny over the mind of man.

```{r}
#| label: tbl-movie-summary
#| tbl-cap: Summary statistics for movies by genre

tbl_summary <- movies |>
  group_by(genre) |>
  summarize(n = n(),
            runtime = mean(runtime),
            metascore = mean(metascore),
            prop_r_rated = mean(maturity_rating == "R"))

gt(tbl_summary) |>
  fmt_percent(prop_r_rated, decimals = 1) |>
  fmt_number(c(runtime, metascore), decimals = 1) |>
  fmt_integer(n) |>
  cols_label(genre = "Genre", 
             n = "Number",
             runtime = "Runtime (minutes)",
             metascore = "Metascore",
             prop_r_rated = "R-rated") |>
  cols_align(genre, align = "left") |>
  tab_spanner(label = "mean value", columns = c(metascore, runtime))
```

I can reference @tbl-movie-summary in the text.
